---
title: "Netflix Userbase Dataset Analysis"
author: "William L."
format: 
  html:
    self-contained: True
---

#### About

The Netflix Userbase Dataset offers a snapshot of a sample of Netflix userbase,
highlighting various aspects such as user subscriptions, revenue, account details,
and activity. Each row corresponds to a unique user, all of which are identified
by their User ID. Expect to see details such as subscription type, monthly
revenue, join date, last payment due, and country.

Additional columns provide insights into user behavior and preferences, such as
Device Type and account status.

#### Intro

I will be utilizing the graphic capabilities from R while delving into the
essential demographic intricacies of Netflix users. Grasping demographics of
users is quite crucial for companies to refine their strategic objectives,
elevate user experience, and enhance marketing initiatives.

#### R Packages

```{r}
library(tidyverse)
library(ggplot2)
library(scales)
library(RColorBrewer)
```

#### Unpacking dataset

This will be the dataset that I intend on using for analysis.

```{r}
netflix <- read.csv("Netflix Userbase.csv")

```

```{r}
# Examining first 5 rows of dataset

head(netflix)

```

```{r}
# Counting number of users for each subscription

netflix %>%
  group_by('Subscription Type') %>%
  summarize('Monthly Revenue' = n())
```

```{r}
df <- data.frame(Type = c("Basic", "Premium", "Standard"),
                 value = c(999, 733, 768))
bp <- ggplot(df, aes(x = "",
                     y = value,
                     fill = Type)) +
  geom_bar(width = 1,
           stat = "identity")
pie1 <- bp + coord_polar ("y", start = 0)
blank_theme <- theme_minimal() + theme(axis.title.x = element_blank(),
                                       axis.title.y = element_blank(),
                                       panel.border = element_blank(),
                                       panel.grid = element_blank(),
                                       axis.ticks = element_blank(),
                                       plot.title = element_text(size = 14,
                                                                 face = 'bold'))
```


#### Distribution of Subscription

```{r}
# Piechart

pie1 + scale_fill_manual(values = c("lightblue", "blue", "navy")) +
  blank_theme + theme(axis.title.x = element_blank(),
                      plot.title = element_text(size = 15)) +
  ggtitle("Distribution of Subscription Type") +
  geom_text(aes(y = value/3 + c(0, cumsum(value) [-length(value)]),
                label = percent(value/2500)), size = 7)
```

```{r}
# Barplot of dataframe

bp <- ggplot(df, aes(x = "",
                     y = value,
                     fill = Gender)) +
  geom_bar(width = 1, stat = "identity")
pie <- bp + coord_polar("y", start = 0)
blank_theme <- theme_minimal() +
  theme(
    axis.title.x = element_blank(),
    axis.title.y = element_blank(),
    panel.border = element_blank(),
    panel.grid = element_blank(),
    axis.ticks = element_blank(),
    plot.title = element_text(size = 15, face = "bold")
  )
```

#### Distribution of Age

```{r}
# Histogram Visualization

p <- netflix %>%
  filter(Age<100) %>%
  ggplot( aes(x= Age)) +
    geom_histogram( binwidth=1, fill="lightblue", color="white", alpha=0.9) +
    ggtitle("Distribution of User Age") +  ylab("Frequency") +
    theme(
      plot.title = element_text(size=14, face = "bold")
    )
p
```

#### Distribution of users via device type

```{r}
data<- netflix %>% group_by (`Device`) %>% summarize (`Device` = n())
data <- data.frame(category = c("Smartphone", "Tablet", "Smart TV", "Laptop"), 
        count = c(636, 610, 621, 633)) 

# Percentage Computation
data$fraction <- (data$count / sum(data$count)) *100

# Cumulative percentages
data$ymax <- cumsum(data$fraction)

# Bottom of each rectangle computation
data$ymin <- c(0, head(data$ymax, n=-1))

# Label Position Computation
data$labelPosition <- (data$ymax + data$ymin) / 2

# Label
data$label <- paste0(data$category, "\n", data$fraction, "%")

# Plot
ggplot(data, aes(ymax=ymax, ymin=ymin, xmax=4, xmin=3, fill=category)) +
  geom_rect(color = "white") +
  geom_label(x=3.5, aes(y=labelPosition, label=label), size=5) +
  ggtitle("Device Distribution")+
  scale_fill_manual(values = c("blue", "#f5f5f1","navy","lightblue")) +
  coord_polar(theta="y") + 
  xlim(c(2, 4)) +
  theme_void() +
  theme(legend.position = "none",  plot.title = element_text(size=14,face = "bold"))
```

```{r}
data_country <- netflix %>% 
count (netflix$Country) %>% 
rename(Country = "netflix$Country") 

data_country <- data_country %>%
  mutate(Country = ifelse(Country == "United States", "USA",
                   ifelse(Country == "United Kingdom", "UK", Country)))

world_map <- map_data ("world")
total_map <- full_join(data_country, world_map, by = c("Country" = "region"))

scale_fill_gradient(
  name = waiver(),
  low = "lightblue",
  high = "navy",
  space = "Lab",
  na.value = "grey50",
  guide = "colourbar",
  aesthetics = "fill"
)
```

#### Users Distribution

```{r}
options(repr.plot.width = 14, repr.plot.height = 8)
ggplot(total_map, aes(long, lat, group=group)) +
  geom_polygon(aes(fill = n),color="white") +
  scale_fill_gradient(low = "lightblue", high = "navy") + 
  theme_void() + 
  ggtitle ('Distribution of Global Users') +
  theme(
  axis.title.x = element_blank(),
  axis.title.y = element_blank(),
  panel.border = element_blank(),
  panel.grid=element_blank(),
  axis.ticks = element_blank(),
  plot.title=element_text(size=15, face="bold")
  )
```

#### Type of Subscription (by country)

```{r}
library(ggplot2)

data_test2 <- data.frame(
  Subscription = rep(c('Basic', 'Premium', 'Standard'), each = 10),
  Country = rep(c('Australia', 'Brazil', 'Canada', 'France', 'Germany', 
                  'Italy', 'Mexico', 'Spain', 'United Kingdom', 'United States'), times = 3),
  Users = c(31, 146, 145, 36, 149, 176, 4, 110, 3, 199,   
            101,  33, 88, 147, 3, 4, 0, 212, 145, 0,  
           51, 4, 84, 0,31,3,179,129,180,107))

ggplot(data_test2, aes(x = Subscription, y = Users, fill = Country)) + theme_void()+
  ggtitle ('Subscription Distribution Per Country') +
  geom_bar(stat = "identity", position = "stack") +
  labs( x = "Subscription Plan", y = "Number of Users") + theme_minimal()+ 
  theme(plot.title=element_text(size=15, face="bold"), 
       axis.title.x = element_text (size = 15), 
       axis.title.y = element_text(size = 15),
       legend.title = element_text (size = 12)
       )
```

